Dynein walks like an Imperial AT-ST

### 2018-08-15 papers/paper/paper.tex
Move to use color_hist2.py to generate 2d histograms
Slight change to eqb

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_time_vs_length}
\caption{Heatmap of relationship between step length and time.}
\label{fig:duration-length}
\end{figure}

>>>>

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

@@
